Figure: the scatterblob

### 2022-03-31 R/scatterblob.Rmd
edits after small group discussion

svg(filename = "scatterblob_0.svg", width = 7, height = 11, bg = "white")

@@

for (i in seq(nrow(scatterblob_data))) {
  X0 <- scatterblob_data$x1[i]
  X1 <- scatterblob_data$x2[i]
  Y <- scatterblob_data$`Cognitive load`[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
    adj_text <- -0.1
   } else {
    adj_text <- 0.5
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 20)
   text(x = median(c(X0, X1)), 
       y = Y, 
       labels = my_data$`Ways to use GitHub`[i],
       adj = adj_text)
}
dev.off()
```
![Fgure 1. Degree of collaboration VS technical difficulty](scatterblob_0.svg)

>>>>

svg(filename = "scatterblob_0.svg", width = 7, height = 15, bg = "white")

@@

for (i in seq(nrow(scatterblob_data))) {
  X0 <- scatterblob_data$x1[i]
  X1 <- scatterblob_data$x2[i]
  Y <- scatterblob_data$`Cognitive load`[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
    adj_text <- -0.1
   } else {
    # adj_text <- 0.5
    adj_text <- 0
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 25)
   text(#x = median(c(X0, X1)),
        x = X1,
       y = Y, 
       labels = my_data$`Ways to use GitHub`[i],
       adj = adj_text)
}
dev.off()
```
![Figure 1. Degree of collaboration VS technical difficulty](scatterblob_0.svg)
